---
title: "Buffett-Style Stock Analysis"
output: html_document
params:
  ticker: "TCS"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
source("R/load_all.R")

report <- analyze_stock(params$ticker)
```

# `r report$ticker`

Report generated on `r format(Sys.Date(), "%d %B %Y")`.

## Part 2: Numbers at a Glance

```{r}
checklist_df <- data.frame(
  Criterion = c(
    "Strong upward EPS trend (10yr)",
    "ROE above 15% (10yr avg)",
    "ROIC/ROCE above 12% (10yr avg)",
    "Long-term debt < 5x Net Income",
    "Free Cash Flow positive (all years)"
  ),
  Result = c(
    ifelse(report$checklist$eps_upward_trend, "Yes", "No"),
    ifelse(report$checklist$roe_above_15, "Yes", "No"),
    ifelse(report$checklist$roic_above_12, "Yes", "No"),
    ifelse(report$checklist$debt_below_5x_ni, "Yes", "No"),
    ifelse(report$checklist$fcf_positive, "Yes", "No")
  )
)
knitr::kable(checklist_df)
```

## Part 3: Is the Price a Cheap Price?

### Stage A — Initial Rate of Return

```{r}
data.frame(
  Metric = c("Current EPS", "Current Price", "Initial Rate of Return"),
  Value = c(
    round(report$stage_a$current_eps, 2),
    round(report$stage_a$current_price, 2),
    paste0(round(report$stage_a$initial_rate_of_return, 2), "%")
  )
) %>% knitr::kable()
```

### Stage B — Expected Return (ROE Method)

```{r}
data.frame(
  Metric = c(
    "Average ROE (10yr)", "Average Payout Ratio (10yr)", "Sustainable Growth Rate",
    "Book Value", "Future Book Value (10yr)", "Future EPS (10yr)",
    "P/E Ratio", "Future Stock Price (10yr)", "Expected Return (ROE Method)"
  ),
  Value = c(
    paste0(round(report$stage_b$avg_roe, 2), "%"),
    paste0(round(report$stage_b$avg_payout, 2), "%"),
    paste0(round(report$stage_b$growth_rate, 2), "%"),
    round(report$stage_b$book_value, 2),
    round(report$stage_b$future_book_value, 2),
    round(report$stage_b$future_eps, 2),
    round(report$stage_b$pe_ratio, 2),
    round(report$stage_b$future_price, 2),
    paste0(round(report$stage_b$expected_return_roe_method, 2), "%")
  )
) %>% knitr::kable()
```

### Stage C — Expected Return (EPS Growth Method)

```{r}
data.frame(
  Metric = c(
    "Current EPS", "EPS Growth Rate (historical)", "Future EPS (10yr)",
    "P/E Ratio", "Future Stock Price (10yr)", "Expected Return (EPS Method)"
  ),
  Value = c(
    round(report$stage_c$current_eps, 2),
    paste0(round(report$stage_c$eps_growth_rate, 2), "%"),
    round(report$stage_c$future_eps, 2),
    round(report$stage_c$pe_ratio, 2),
    round(report$stage_c$future_price, 2),
    paste0(round(report$stage_c$expected_return_eps_method, 2), "%")
  )
) %>% knitr::kable()
```

### Stage D — Final Verdict

```{r}
verdict_color <- switch(report$stage_d$verdict,
  "FANTASTIC" = "green",
  "GOOD" = "darkorange",
  "UNACCEPTABLE" = "red"
)
```

**Average Expected Return:** `r round(report$stage_d$avg_expected_return, 2)`%

**Verdict:** <span style="color:`r verdict_color`; font-weight:bold; font-size:1.3em;">`r report$stage_d$verdict`</span>

---

*This report is generated for educational purposes based on publicly available data from Screener.in. It is not investment advice.*