---
title: "Buffett-Style Stock Analysis"
output: html_document
params:
  ticker: "TCS"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
source("R/load_all.R")

report <- analyze_stock(params$ticker)
```

# `r report$ticker`

Report generated on `r format(Sys.Date(), "%d %B %Y")`.

## Part 2: Numbers at a Glance

```{r}
checklist_df <- data.frame(
  Criterion = c(
    "Strong upward EPS trend (10yr)",
    "ROE above 15% (10yr avg)",
    "ROIC/ROCE above 12% (10yr avg)",
    "Long-term debt < 5x Net Income",
    "Free Cash Flow positive (all years)"
  ),
  Result = c(
    ifelse(report$checklist$eps_upward_trend, "Yes", "No"),
    ifelse(report$checklist$roe_above_15, "Yes", "No"),
    ifelse(report$checklist$roic_above_12, "Yes", "No"),
    ifelse(report$checklist$debt_below_5x_ni, "Yes", "No"),
    ifelse(report$checklist$fcf_positive, "Yes", "No")
  )
)
knitr::kable(checklist_df)
```

## Part 3: Is the Price a Cheap Price?

### Stage A — Initial Rate of Return

```{r}
data.frame(
  Metric = c("Current EPS", "Current Price", "Initial Rate of Return"),
  Value = c(
    round(report$stage_a$current_eps, 2),
    round(report$stage_a$current_price, 2),
    paste0(round(report$stage_a$initial_rate_of_return, 2), "%")
  )
) %>% knitr::kable()
```

### Stage B — Expected Return (ROE Method)

```{r}
data.frame(
  Metric = c(
    "Average ROE (10yr)", "Average Payout Ratio (10yr)", "Sustainable Growth Rate",
    "Book Value", "Future Book Value (10yr)", "Future EPS (10yr)",
    "P/E Ratio", "Future Stock Price (10yr)", "Expected Return (ROE Method)"
  ),
  Value = c(
    paste0(round(report$stage_b$avg_roe, 2), "%"),
    paste0(round(report$stage_b$avg_payout, 2), "%"),
    paste0(round(report$stage_b$growth_rate, 2), "%"),
    round(report$stage_b$book_value, 2),
    round(report$stage_b$future_book_value, 2),
    round(report$stage_b$future_eps, 2),
    round(report$stage_b$pe_ratio, 2),
    round(report$stage_b$future_price, 2),
    paste0(round(report$stage_b$expected_return_roe_method, 2), "%")
  )
) %>% knitr::kable()
```

### Stage C — Expected Return (EPS Growth Method)

```{r}
data.frame(
  Metric = c(
    "Current EPS", "EPS Growth Rate (historical)", "Future EPS (10yr)",
    "P/E Ratio", "Future Stock Price (10yr)", "Expected Return (EPS Method)"
  ),
  Value = c(
    round(report$stage_c$current_eps, 2),
    paste0(round(report$stage_c$eps_growth_rate, 2), "%"),
    round(report$stage_c$future_eps, 2),
    round(report$stage_c$pe_ratio, 2),
    round(report$stage_c$future_price, 2),
    paste0(round(report$stage_c$expected_return_eps_method, 2), "%")
  )
) %>% knitr::kable()
```

### Stage D — Final Verdict (Price Only)

```{r}
verdict_color <- switch(report$stage_d$verdict,
  "FANTASTIC" = "green",
  "GOOD" = "darkorange",
  "UNACCEPTABLE" = "red"
)
```

**Average Expected Return:** `r round(report$stage_d$avg_expected_return, 2)`%

**Verdict:** <span style="color:`r verdict_color`; font-weight:bold; font-size:1.3em;">`r report$stage_d$verdict`</span>

*Greater than 20% = Fantastic · 12-20% = Good · Below 12% = Unacceptable*

### Stage E — Return Scenarios Across Historical PE Range

```{r}
knitr::kable(report$stage_e)
```

### Stage F — Total Return (Price Appreciation + Dividends)

```{r}
knitr::kable(report$stage_f)
```

### Stage G — Final Verdict (Including Dividends)

```{r}
verdict_color_g <- switch(report$stage_g$verdict,
  "FANTASTIC" = "green",
  "GOOD" = "darkorange",
  "UNACCEPTABLE" = "red"
)
```

**Average Total Expected Return:** `r round(report$stage_g$avg_total_expected_return, 2)`%

**Final Verdict (Including Dividends):** <span style="color:`r verdict_color_g`; font-weight:bold; font-size:1.3em;">`r report$stage_g$verdict`</span>

*This verdict is more complete than Stage D's, since it accounts for both price appreciation and dividends. Where the two disagree, this one should generally be treated as the more accurate picture.*

---

## Projected Dividends

```{r}
knitr::kable(report$dividends$table)
```

**Total dividends over `r nrow(report$dividends$table)` years (ROE Method):** ₹`r report$dividends$total_dividend_roe_method` per share

**Total dividends over `r nrow(report$dividends$table)` years (EPS Method):** ₹`r report$dividends$total_dividend_eps_method` per share

*This is a projection based on historical averages, not a guarantee — actual payout policy can and does change.*

---

*This report is generated for educational purposes based on publicly available data from Screener.in and Yahoo Finance (via tidyquant). It is not investment advice.*